## Lab assignment 2: Social network analysis and modeling

```{r}
library('igraph')
library('network')
library('intergraph')
```

Type any R code in the chunk, for example:
```{r}
#read data from the folder data
highschool_edge<-read.csv("Human_networks/Assignment_2_kate/data/Highschool_network_edge.csv")
highschool_att <- read.csv("Human_networks/Assignment_2_kate/data/Highschool_network_att.csv")
facebook_att <- read.csv("Human_networks/Assignment_2_kate/data/Facebook_network_att.csv")
facebook_edge <- read.csv("Human_networks/Assignment_2_kate/data/Facebook_network_edge.csv")
#check that it works!
```
```{r}
highschool_att

```


```{r}
#build high school network
highschool_nodes<-data.frame(name=as.character(highschool_att$NodeID),
                  gender=as.character(highschool_att$Gender),
                  hall=as.character(highschool_att$Hall))
highschool_edges<-data.frame(from=c(as.character(highschool_edge[,1])),
                  to=c(as.character(highschool_edge[,2])))
Highschool<-graph_from_data_frame(highschool_edges,directed = FALSE,vertices = highschool_nodes)
co <- components(Highschool)
Highschool <- induced.subgraph(Highschool, which(co$membership == which.max(co$csize))) #use only the largest component for analysis
summary(Highschool)

#build facebook network
facebook_nodes<-data.frame(name=as.character(facebook_att$NodeID))
facebook_edges<-data.frame(from=c(as.character(facebook_edge[,1])),
                           to=c(as.character(facebook_edge[,2])))
Facebook<-graph_from_data_frame(facebook_edges,directed = FALSE,vertices = facebook_nodes)
summary(Facebook)
```


```{r}

#function to visualize the network (with interaction)
library(visNetwork)
set.seed(100)
Highschool_interactive_layout<-visNetwork(data.frame(id=V(Highschool)$name), highschool_edges, main = "Highschool",submain="Can zoom in/out to check the IDs and ties") %>%
  visIgraphLayout(layout = "layout_nicely",smooth =  FALSE) %>%
  visNodes(shape="circle",label = TRUE) %>%
  visOptions(highlightNearest = list(enabled = T, hover = T), nodesIdSelection = T)

Highschool_interactive_layout

```
```{r}

# find the node of he hisghest degree
#degree(Highschool)
which.max(degree(Highschool))
V(Highschool)[which.max(degree(Highschool))]
#get the top-3 nodes with the highest degree
degree(Highschool)[order(degree(Highschool),decreasing = TRUE)][1:3]

```

```{r}
#find the node of the highest betweenness centrality
#
which.max(betweenness(Highschool))
V(Highschool)[which.max(betweenness(Highschool))]
# #top-3 nodes with the highest betweenness centrality
# betweenness(Highschool)[order(betweenness(Highschool),decreasing = TRUE)][1:3]

```
```{r}
betweenness(Highschool)[order(betweenness(Highschool),decreasing = TRUE)][1:3]
```
```{r}
#find the node of the highest closeness centrality
#closeness(Highschool)
which.max(closeness(Highschool))
V(Highschool)[which.max(closeness(Highschool))]

```
```{r}
#find the node with the highest eigen
ec <- eigen_centrality(Highschool)

# Find the node(s) with the highest eigen centrality
highest_ec <- which(ec$vector == max(ec$vector))
highest_ec
```


Question 2 (5 points):
•	Study the correlations between a) degree and betweenness, b) degree and closeness, c) degree and eigenvector for all the nodes in the Highschool network;
•	Study the correlations between a) degree and betweenness, b) degree and closeness, c) degree and eigenvector for all the nodes in the Facebook network;
•	From the above results, how well do different metrics correlate with each other? Which centrality metric will you use and why?
Please provide more than just a correlation coefficient to answer Question 2. You are suggested to study the correlations by developing a scatter plot as below, in which every dot represents a node in the network, with xlab as degree and ylab as closeness.
```{r}
#check the correlation between degree and betweenness
cor.test(degree(Highschool),betweenness(Highschool))
```
```{r}
#check the correlation between degree and closeness
cor.test(degree(Highschool),closeness(Highschool))
```
```{r}
#check the correlation between degree and eigenvector
eigen_hs <- eigen_centrality(Highschool)$vector
cor.test(degree(Highschool),eigen_hs)
```
```{r}
#check the correlation between degree and betweenness
cor.test(degree(Facebook),betweenness(Facebook))
```
```{r}
#check the correlation between degree and closeness
cor.test(degree(Facebook),closeness(Facebook))
```
```{r}
#check the correlation between degree and eigenvector and add the trand line
eigen_fb <- eigen_centrality(Facebook)$vector
cor.test(degree(Facebook),eigen_fb)
```
```{r}
#make a scatter plot for degree and closeness and add the trand line
plot(degree(Highschool),closeness(Highschool),xlab="Degree",ylab="Closeness")
abline(lm(closeness(Highschool)~degree(Highschool)),col="red")
#make the confident interval for the trand line with grey color
```



```{r}
#make a scatter plot for degree and closeness for Facebook
plot(degree(Highschool),betweenness(Highschool),xlab="Degree",ylab="Betweenness")
abline(lm(betweenness(Highschool)~degree(Highschool)),col="red")
```
```{r}
#make a plot for correlation between degree and eigenvector
plot(degree(Highschool),eigen_hs,xlab="Degree",ylab="Eigenvector")
abline(lm(eigen_hs~degree(Highschool)),col="red")
```
```{r}
#make a scatter plot for degree and closeness for Facebook
plot(degree(Facebook),closeness(Facebook),xlab="degree",ylab="closeness")
abline(lm(closeness(Facebook)~degree(Facebook)),col="red")
```
```{r}
#make a scatter plot for degree and betweenness for Facebook
plot(degree(Facebook),betweenness(Facebook),xlab="degree",ylab="betweenness")
abline(lm(betweenness(Facebook)~degree(Facebook)),col="red")
```
```{r}
#make a plit for correlation between degree and eigenvector for Facebook
plot(degree(Facebook),eigen_fb,xlab="degree",ylab="eigenvector")
abline(lm(eigen_fb~degree(Facebook)),col="red")
```
```{r}
# calculate the shortest path lengths between every pair of two nodes in Highschool network

distances(
  Highschool,
  v = V(Highschool),
  to = V(Highschool),
  mode = c("all", "out", "in"),
  weights = NULL) #Shortest path lengths between every pair of two nodes in the network

```
```{r}
#make a histogram of the shortest path lengths between every pair of two nodes in Highschool network with percentiles
hist(distances(Highschool),xlab="shortest path length",ylab="% of total cout by group",main="Histogram of the shortest path lengths between every pair of two nodes in Highschool network",breaks=10,prob=T)
#add percentiles and add the value of the percentiles to the plot
abline(v=quantile(distances(Highschool),c(0.25,0.5,0.75)),col="red")
text(quantile(distances(Highschool),c(0.25,0.5,0.75)),c(0.1,0.1,0.1),labels=quantile(distances(Highschool),c(0.25,0.5,0.75)),col="red")
```
```{r}
hist(distances(Facebook),xlab="shortest path length",ylab="% of total cout by group",main="Histogram of the shortest path lengths between every pair of two nodes in Facebook network",breaks=10,prob=T)
#add percentiles and add the value of the percentiles to the plot
abline(v=quantile(distances(Facebook),c(0.25,0.5,0.75)),col="red")
text(quantile(distances(Facebook),c(0.25,0.5,0.75)),c(0.1,0.1,0.1),labels=quantile(distances(Facebook),c(0.25,0.5,0.75)),col="red")
```


Test the above hypothesis by the following steps (Question 4, 4 points):
```{r}
#visualize the Highschool network by gender
library(RColorBrewer)
coul  <- brewer.pal(length(unique( V(Highschool)$gender)), "Set2")
my_color <- coul[as.numeric(as.factor(V(Highschool)$gender))]
set.seed(10)
plot(Highschool, vertex.color = my_color,
     vertex.size=5,
     layout=layout.fruchterman.reingold(Highschool),vertex.label=NA,
     main="Highschool network by gender")
#add the legend of the color of the nodes
legend("bottomleft", legend=levels(as.factor(V(Highschool)$gender)) ,col = coul , bty = "n", pch=20 , pt.cex = 2, cex = 1.5, horiz = FALSE, inset = c(0.1, 0.1))
#show the graph with only nodes where gender is femake

```


```{r}
#visualize the Highschool network by residentil area
coul  <- brewer.pal(length(unique(V(Highschool)$hall)), "Set2")
my_color <- coul[as.numeric(as.factor(V(Highschool)$hall))]
set.seed(10)
plot(Highschool, vertex.color = my_color,
     vertex.size=5,
     layout=layout.fruchterman.reingold(Highschool),vertex.label=NA,
     main="Highschool network by Hall")
#add the legend of the color of the nodes at the top left corner
legend("bottomleft", legend=levels(as.factor(V(Highschool)$gender)) ,col = coul , bty = "n", pch=20 , pt.cex = 1.5, cex = 1.5, horiz = FALSE, inset = c(0.1, 0.1))
```

```{r}
#introduce subgraph by gender = F, calculate their edge densities
group_female <- as.factor(unique(V(Highschool)$gender=='female'))
sapply(levels(group_female), function(x) {
  y <- induced_subgraph(Highschool, which(V(Highschool)$gender==x))
  paste0("Density for ", x, " friends is ", edge_density(y))
})



```
```{r}
group <- as.factor(unique(V(Highschool)$hall))
sapply(levels(group), function(x) {
  y <- induced_subgraph(Highschool, which(V(Highschool)$hall==x))
  paste0("Density for ", x, " friends is ", edge_density(y))
})
```
```{r}
#introduce subgraph by gender, calculate their edge densities
group <- as.factor(unique(V(Highschool)$gender))
sapply(levels(group), function(x) {
  y <- induced_subgraph(Highschool, which(V(Highschool)$gender==x))
  paste0("Density for ", x, " friends is ", edge_density(y))
})

```
```{r}
#overall density of the network
edge_density(Highschool)
```
```{r}
```
## Question 5 (4 points):
1)	Calculate the modularity of the Highschool network if community is merely identified by a) gender and b) residential hall, respectively.
2)	Search the Louvain Community Detection and explain the algorithm in your own words.
3)	Use the Louvain Community Detection to identify communities in the Highschool network. Compare the modularity value produced by the Louvain algorithm to those in 1), and explain the reasons for the differences.
```{r}
### customize community by gender

genderCommunity<-V(Highschool)$gender
genderCommunity<-replace(genderCommunity,genderCommunity=="female",1)
genderCommunity<-replace(genderCommunity,genderCommunity=="male",2)
genderCommunity<-replace(genderCommunity,genderCommunity=="unknown",3)
genderCommunity<-as.numeric(genderCommunity)

gender.clustering <- make_clusters(Highschool, membership=genderCommunity)
modularity(gender.clustering)

```
```{r}
### customize community by hall
hallCommunity<-V(Highschool)$hall
hallCommunity<-replace(hallCommunity,hallCommunity=="1501",1)
hallCommunity<-replace(hallCommunity,hallCommunity=="1502",2)
hallCommunity<-replace(hallCommunity,hallCommunity=="1503",3)
hallCommunity<-replace(hallCommunity,hallCommunity=="1504",4)
hallCommunity<-replace(hallCommunity,hallCommunity=="1505",5)
hallCommunity<-as.numeric(hallCommunity)

hall.clustering <- make_clusters(Highschool, membership=hallCommunity)
modularity(hall.clustering)

```
```{r}
### Louvain algorithm ###
Louv<-cluster_louvain(Highschool)
modularity(Louv)

```
```{r}
### Louvain algorithm ###
# Louv<-cluster_louvain(Facebook)
# modularity(Louv)
```
Exercise two: Network formation models
Network relationships come in many shapes and sizes, and so there is no single model which encompasses them all.
But over time, people do summarize some common paradigm that can be used to build a synthetic network.
In the lecture, we mentioned three major architectures to build a synthetic network, which is Erdos-Renyi Random Graph Model,
Small-world Random Graph Model, and Barabasi-Albert (BA) model.


```{r}

sample_gnp(20, 0.1, directed = FALSE, loops = FALSE)
#visualize the network
plot(sample_gnp(20, 0.1, directed = FALSE, loops = FALSE),vertex.label=NA)
#add the name of the plot
title(main="ER1")
```
```{r}
ER1 <-sample_gnp(20, 0.1, directed = FALSE, loops = FALSE)
plot((ER1), vertex.label=NA)
#add the name of the plot
title(main="ER1")
```
```{r}

ER2 <- sample_gnp(20, 0.2, directed = FALSE, loops = FALSE)
plot((ER2),vertex.label=NA)
#add the name of the plot
title(main="ER2")
```
```{r}
ER3 <-sample_gnp(20, 0.3, directed = FALSE, loops = FALSE)
plot((ER2),vertex.label=NA)
#add the name of the plot
title(main="ER3")
```
```{r}
#average degree of the ER1
mean(degree(ER1))
```
```{r}
#average length path of the ER1
mean_distance(ER3)
```
```{r}
#cluster coefficient of the ER1
transitivity(ER3)
```
```{r}
mean(degree(ER2))
```
```{r}
mean(degree(ER3))
```
```{r}
#minimum degree of the ER1
min(degree(ER1))
```
```{r}
min(degree(ER2))
```
```{r}
min(degree(ER3))
```
```{r}
#maximum degree of the ER1
max(degree(ER1))
```
```{r}
max(degree(ER2))
```
```{r}
max(degree(ER3))
```
```{r}
ER1000 <-sample_gnp(1000, 0.1, directed = FALSE, loops = FALSE)
plot((ER1000), vertex.label=NA)
#add the name of the plot
title(main="ER1000")

```
```{r}
transitivity(ER1000)
```
```{r}
ER1000_2 <-sample_gnp(1000, 0.2, directed = FALSE, loops = FALSE)
ER1000_3 <-sample_gnp(1000, 0.3, directed = FALSE, loops = FALSE)
ER1000_4 <-sample_gnp(1000, 0.4, directed = FALSE, loops = FALSE)
ER1000_5 <-sample_gnp(1000, 0.5, directed = FALSE, loops = FALSE)
ER1000_9 <-sample_gnp(1000, 0.9, directed = FALSE, loops = FALSE)
# plot((ER1000_2), vertex.label=NA)
#add the name of the plot
# title(main="ER1000_2")

```
```{r}
# transitivity(ER1000_2)
transitivity(ER1000_9)
```
```{r}
Regular<-watts.strogatz.game(dim=1,size=300,nei=6, p=0)
plot(Regular, layout=layout.circle, vertex.label=NA, vertex.size=5, main= "Network with zero rewiring probability ")
SW1<-watts.strogatz.game(dim=1,size=300,nei=6, p=0.001)
plot(SW1, layout=layout.circle, vertex.label=NA, vertex.size=5, main= "Network with 0.001 rewiring probability ")
SW2<-watts.strogatz.game(dim=1,size=300,nei=6, p=0.01)
plot(SW2, layout=layout.circle, vertex.label=NA, vertex.size=5, main= "Network with 0.01 rewiring probability ")
SW3<-watts.strogatz.game(dim=1,size=300,nei=6, p=0.1)
plot(SW3, layout=layout.circle, vertex.label=NA, vertex.size=5, main= "Network with 0.1 rewiring probability ")

```
```{r}
transitivity(Regular)
```
```{r}
transitivity(SW1)
```
```{r}
transitivity(SW2)
```
```{r}
transitivity(SW3)
```
```{r}
#calculate teh averahe path length
mean_distance(Regular)
```
```{r}
mean_distance(SW1)
```
```{r}
mean_distance(SW2)
```
```{r}
mean_distance(SW3)

```
```{r}
Regular8<-watts.strogatz.game(dim=1,size=300,nei=6, p=0)
plot(Regular8, layout=layout.circle, vertex.label=NA, vertex.size=5, main= "Network with zero rewiring probability ")
```
```{r}
#make the previos plot in y range from 0 to 1
p<-seq(0,1,0.01)
mean_distance<-c()
clustering<-c()
for (i in p){
  Regular8<-watts.strogatz.game(dim=1,size=300,nei=6, p=i)
  mean_distance<-c(mean_distance,mean_distance(Regular8))
  clustering<-c(clustering,transitivity(Regular8))
}
par(mfrow = c(1, 2))

plot(p,mean_distance,xlab="Rewiring probability",ylab="Average path length",ylim=c(0,1))
plot(p,clustering,col="red", xlab="Rewiring probability",ylab="Clustering",ylim=c(0,1))
legend("topright",c("Average path length","Clustering coefficient"),col=c("black","red"),lty=1)

```
```{r}
g0 <- barabasi.game(100, power =  0.1, m = NULL, out.dist = NULL, out.seq = NULL, out.pref = FALSE, zero.appeal = 1, directed = FALSE,algorithm ="psumtree", start.graph = NULL)
plot(g0, vertex.label= NA, edge.arrow.size=0.02,vertex.size =5, main = "Scale-free network model, power=1")


```

Exercise three: Simulation of simple and complex contagion
In this exercise, you will simulate the spread of simple and complex contagion in the Highschool network.

For the Highschool network, identify five edges which after deletion, there will be significant gain of the average path lengths of the network.
In other words, if such five edges did not exist, the average path length of the network would increase significant.
Provide your answer in the format of A-B, in which A and B are the node ID. Are they weak ties or strong ties? (Question 10, 2 points)
```{r}
#calculate 5 edges with the highest betweenness centrality in Highschool network
edge_betweenness <- edge_betweenness(Highschool)
top_5_edges <- sort(edge_betweenness, decreasing = TRUE)[1:5]
top_5_edges_indices <- which(edge_betweenness %in% top_5_edges)
top_5_edges <- as_edgelist(Highschool)[top_5_edges_indices,]
top_5_edges
```

```{r}
stopifnot(require(data.table))
stopifnot(require(Matrix))

calculate_value <- function(node, each_neighbors,Pprob){
  return(each_neighbors[[node]][ which(runif(length(each_neighbors[[node]]), 0, 1)<=Pprob)])
  #'runif' is a function to generate random number in R
}
#This function:
#1) searches the neighbors of contagious node;
#2) To those who are connected to a contagious node, generates a random number and compare to the
#probability of p, if random number<p, this node will be infected and return the value of 1

IC<-function(node_seed,network,Pprob){

  #prepare input for the 'calculate_value' function#
  adj_matrix <- igraph::as_adjacency_matrix(network, type = 'both')
  each_neighbors <- which(adj_matrix > 0, arr.ind = TRUE)
  each_neighbors <- split(each_neighbors[, 2], each_neighbors[, 1]) #get the neigbhour list of each node

  nNode<-vcount(network)
  node_status <- rep.int(0, nNode) #start from a healthy population
  day_infected<-vector()#Total number of infected population
  new_infected <- list()  # Record the ID of person getting infected at each time step

  day<-1
  node_status[as.numeric(node_seed)] <- 1 # infected(value=1) health(value=0)
  day_infected[day] <- sum(node_status)
  new_infected[[day]]<-node_seed #The ID of the person infected in Day 1 (Patient Zero)

  #simulate the spread of virus within 4 weeks##
  for (day in c(2:28)){
    ContagiousID<-which(node_status == 1)
    #print(ContagiousID) #инфцированные ноды
    infectedID<-unlist(lapply(ContagiousID,calculate_value,each_neighbors,Pprob))
    # print('кого заразили')
    # print(infectedID) #кого заразили
    newinfectedID<- setdiff(infectedID, which(node_status == 1))
    # print('новенькие')
    # print(newinfectedID)
    #print(newinfectedID) #вывести новых зараженных

    #Update the node status and other variables
    node_status[newinfectedID] <- 1
    day_infected[day] <- length(newinfectedID)
    # print(day_infected[day])

    new_infected[[day]]<-newinfectedID
    day=day+1
  }
  return(day_infected)  #return the number of newly infected people by day
  #return(list(day_infected,new_infected)) #if you want to see the ID of infected ppl in each day, use this command instead
}

```
```{r}
IC(5, Highschool, 0.15)
```
```{r}
# IC(5, Highschool, 0.15)

# run the IC model 100 times and take the average
IC_average <- function(node_seed,network,Pprob){
  n <- 100
  result <- matrix(0, nrow = 28, ncol = n)
  for (i in 1:n){
    result[, i] <- IC(node_seed,network,Pprob)
  }
  return(apply(result, 1, mean))
}


```
```{r}
sum(IC_average(5, Highschool, 0.15))


```
```{r}
#plot IC_average(5, Highschool, 0.15)
plot(IC_average(5, Highschool, 0.15), type = "l", ylim = c(0, 10), xlab = "Day", ylab = "Average number of infected people (IC)")

```
```{r}
#delete the the nodes with the highest betweenness centrality
Highschool2 <- delete_vertices(Highschool, top_5_edges)
```
```{r}
#delete the edhe between 5 and 6 and 5 and 7
# Highschool3 <- delete_edges(Highschool, c(60, 44, 12, 24, 96, 94, 43, 90,46,58))
Highschool3 <- delete_edges(Highschool, c(54, 112, 20, 50, 110, 10, 64, 61,96,94))
# strongest_edges <- sort(degree(Highschool), decreasing = TRUE)[1:5]
# strongest_edges
# Highschool3 <- delete.edges(Highschool, strongest_edges)
```


```{r}
sum(IC_average(5, Highschool2, 0.15))
```
```{r}
sum(IC_average(5, Highschool3, 0.15))
```
```{r}
#make a plot of the average number of infected people by day for Highschool, Highschool2, and Highschool3
#add color to the lines to distinguish the three networks
plot(IC_average(5, Highschool, 0.15), type = "l", col = "red", ylim = c(0, 10), xlab = "Day", ylab = "Average number of infected people", lwd = 4)
lines(IC_average(5, Highschool2, 0.15), type = "l", col = "blue", lwd = 4)
lines(IC_average(5, Highschool3, 0.15), type = "l", col = "green", lwd = 4)
legend("topright", c("Highschool - original", "Highschool2 - weak ties", "Highschool3 - strong ties"), col = c("red", "blue", "green"), lty = 1)

```

```{r}
plot(IC_average(5, Highschool, 0.8), type = "l", col = "red",lwd = 4, ylim = c(0, 36), xlab = "Day", ylab = "Average number of infected people")
lines(IC_average(5, Highschool2, 0.8), type = "l", col = "blue", lwd = 4)
lines(IC_average(5, Highschool3, 0.8), type = "l", col = "green", lwd = 4)
legend("topright", c("Highschool - original", "Highschool2 - weak ties", "Highschool3 - strong ties"), col = c("red", "blue", "green"), lty = 1)
```
```{r}
#make a SIR model from the previous IC model
SIR <-function(node_seed,network,Pprob){

  #prepare input for the 'calculate_value' function#
  adj_matrix <- igraph::as_adjacency_matrix(network, type = 'both')
  each_neighbors <- which(adj_matrix > 0, arr.ind = TRUE)
  each_neighbors <- split(each_neighbors[, 2], each_neighbors[, 1]) #get the neigbhour list of each node

  nNode<-vcount(network)
  # node_status <- rep.int(0, nNode) #start from a healthy population
  node_status <- data.frame(status=rep(0, nNode), infected_day=NA) #start from a healthy population
  day_infected<-vector()#Total number of infected population
  new_infected <- list()  # Record the ID of person getting infected at each time step

  day<-1
  node_status[as.numeric(node_seed), "status"] <- 1 # infected(value=1) health(value=0)
  node_status[as.numeric(node_seed), "infected_day"] <- day
  day_infected[day] <- sum(node_status$status)
  new_infected[[day]]<-node_seed #The ID of the person infected in Day 1 (Patient Zero)

  #simulate the spread of virus within 4 weeks##
  for (day in c(2:28)){
    contagious_nodes <- which(node_status$status == 1 & (day - node_status$infected_day) < 4)
    infected_nodes<-unlist(lapply(contagious_nodes,calculate_value,each_neighbors,Pprob))
    newinfected_nodes<- setdiff(infected_nodes, which(node_status$status > 0))

    #Update the node status and other variables
    node_status[newinfected_nodes, "status"] <- 1
    node_status[newinfected_nodes, "infected_day"] <- day
    day_infected[day] <- length(newinfected_nodes)
    new_infected[[day]]<-newinfected_nodes

    # Mark nodes as recovered if they have been infected for 3 days
    recovered_nodes <- which(node_status$status == 1 & (day - node_status$infected_day) == 3)
    node_status[recovered_nodes, "status"] <- 2

    day=day+1
  }
  return(day_infected)  #return the number of newly infected people by day
  #return(list(day_infected,new_infected)) #if you want to see the ID of infected ppl in each day, use this command instead
}

```
```{r}
SIR(5, Highschool, 0.15)
```
```{r}
SIR_average <- function(node_seed,network,Pprob){
  n <- 100
  result <- matrix(0, nrow = 28, ncol = n)
  for (i in 1:n){
    result[, i] <- SIR(node_seed,network,Pprob)
  }
  return(apply(result, 1, mean))
}
```
```{r}
sum(SIR_average(5, Highschool, 0.15))
```
```{r}
sum(SIR_average(5, Highschool2, 0.15))
```
```{r}
sum(SIR_average(5, Highschool3, 0.15))
```
```{r}
plot(SIR_average(5, Highschool, 0.15), type = "l", col = "red", lwd = 4, ylim = c(0, 15), xlab = "Day", ylab = "Average number of infected people")
lines(SIR_average(5, Highschool2, 0.15), type = "l", col = "blue", lwd = 4)
lines(SIR_average(5, Highschool3, 0.15), type = "l", col = "green", lwd = 4)
legend("topright", c("Highschool - original", "Highschool2 - weak ties", "Highschool3 - strong ties"), col = c("red", "blue", "green"), lty = 1)
```
```{r}
plot(SIR_average(5, Highschool, 0.5), type = "l", col = "red", lwd = 4, ylim = c(0, 25), xlab = "Day", ylab = "Average number of infected people")
lines(SIR_average(5, Highschool2, 0.5), type = "l", col = "blue", lwd = 4)
lines(SIR_average(5, Highschool3, 0.5), type = "l", col = "green", lwd = 4)
legend("topright", c("Highschool - original", "Highschool2 - weak ties", "Highschool3 - strong ties"), col = c("red", "blue", "green"), lty = 1)
```
```{r}
plot(SIR_average(5, Highschool, 0.1), type = "l", lwd = 4, col = "red", ylim = c(0, 10), xlab = "Day", ylab = "Average number of infected people")
lines(SIR_average(5, Highschool2, 0.1), type = "l", col = "blue", lwd = 4)
lines(SIR_average(5, Highschool3, 0.1), type = "l", col = "green", lwd = 4)
legend("topright", c("Highschool - original", "Highschool2 - weak ties", "Highschool3 - strong ties"), col = c("red", "blue", "green"), lty = 1)
```
```{r}
plot(SIR_average(5, Highschool, 0.8), type = "l", lwd = 4, col = "red", ylim = c(0, 38), xlab = "Day", ylab = "Average number of infected people")
lines(SIR_average(5, Highschool2, 0.8), type = "l", col = "blue", lwd = 4)
lines(SIR_average(5, Highschool3, 0.8), type = "l", col = "green", lwd = 4)
legend("topright", c("Highschool - original", "Highschool2 - weak ties", "Highschool3 - strong ties"), col = c("red", "blue", "green"), lty = 1)
```
```{r}
calculate_adoptedNei <- function(node, node_status, each_neighbors){
  return(mean(node_status[each_neighbors[[node]]] == 1)) ### to calculate the percentage of adopted neigbhours
}

ThModel<-function(node_seed,network,threshold){
  #prepare input for the 'calculate_value' function#
  adj_matrix <- igraph::as_adjacency_matrix(network, type = 'both')
  each_neighbors <- which(adj_matrix > 0, arr.ind = TRUE)
  each_neighbors <- split(each_neighbors[, 2], each_neighbors[, 1]) #get the neigbhour list of each node

  nNode<-vcount(network)
  node_status <- rep.int(0, nNode)
  neighbour_status<-rep.int(0, nNode)  ##percentage of adopted neighbours
  new_infected <- list()
  day_total_infected <- rep(0,28) ### Total number of active people by end of each day


  ### Day 1 ####
  day <- 1
  node_status[as.numeric((node_seed))] <- 1
  new_infected[[day]] <-node_seed
  day_total_infected[day]=sum(node_status == 1)
  ####

  for (day in c(2:28)){
    NotAdopted <- which(node_status == 0)
    Adopted <- which(node_status == 1)

    neighbour_status[NotAdopted] <- unlist(lapply(NotAdopted, calculate_adoptedNei, node_status, each_neighbors))

    new_infected[[day]] <- setdiff(which(neighbour_status > threshold), Adopted)
    node_status[new_infected[[day]]] <- 1  #update the staus to 1 for those newly adopted
    day_total_infected[day] <- sum(node_status)
    #print(new_infected[[day]])
    day <- day + 1
  }
  return(day_total_infected)
  # return(list(day_total_infected,new_infected))

}

```
```{r}
values <- list(59,63,91,92,99)


```
```{r}

ThModel(values, Highschool,highschool_att$Threshold)

```
```{r}
dist <- read.csv("/Users/ekaterinamazur/PycharmProjects/HN/Human_Networks/Assignment_2_kate/data/distribution.csv")
# Calculate the cumulative distribution function (CDF)
cdf <- cumsum(dist$NumberOfStudents) / sum(dist$NumberOfStudents)

# Generate a sample of values between 0 and 1
n_obs <- 122  # Set the number of observations
u <- runif(n_obs)

# Map the values to the corresponding thresholds using the CDF
thresholds <- numeric(n_obs)
for (i in 1:n_obs) {
  idx <- which(u[i] <= cdf)[1]
  # Convert the categorical thresholds to numeric values
  if (dist$Threshold[idx] == ">=10") {
    thresholds[i] <- 10
  } else {
    thresholds[i] <- as.numeric(dist$Threshold[idx])
  }
}

# Count the number of observations for each threshold
counts <- table(thresholds)

# Print the counts for each threshold
print(counts)

thresholds_rand <- sample(thresholds)
thresholds_norm <- scale(thresholds_rand, center = FALSE, scale = diff(range(thresholds_rand, na.rm = TRUE)))
# thresholds_norm
# hist(as.numeric(thresholds_rand), breaks=100)

```
```{r}
highschool_att_beef <- read.csv("Highschool_network_att.csv", header = TRUE)
highschool_att_beef$Threshold <- thresholds_rand
highschool_nodes_beef <- data.frame(name = as.character(highschool_att_beef$NodeID),
                             gender = as.character(highschool_att_beef$Gender),
                             hall = as.character(highschool_att_beef$Hall),
                             threshold = as.numeric(highschool_att_beef$Threshold))
highschool_edges_beef <- data.frame(from = c(as.character(highschool_edge[,1])),
                             to = c(as.character(highschool_edge[,2])))
Highschool_beef <- graph_from_data_frame(highschool_edges_beef,directed = FALSE,vertices = highschool_nodes_beef)
coo <- components(Highschool_beef)
Highschool_beef <- induced.subgraph(Highschool_beef, which(co$membership == which.max(coo$csize))) #use only the largest component for analysis
summary(Highschool_beef)
```

```{r}
th1 <- ThModel(c(59,63,91,92,99),Highschool_beef, thresholds_rand)
th1
```


QUESTION FOUR


```{r}
betweenness(Highschool)[order(betweenness(Highschool),decreasing = TRUE)][1:3]
```
```{r}
#top-3 nodes with the highest degree
degree(Highschool)[order(degree(Highschool),decreasing = TRUE)][1:3]
```
```{r}
calculate_value <- function(node, each_neighbors,Pprob){
  return(each_neighbors[[node]][ which(runif(length(each_neighbors[[node]]), 0, 1)<=Pprob)])
  #'runif' is a function to generate random number in R
}
#This function:
#1) searches the neighbors of contagious node;
#2) To those who are connected to a contagious node, generates a random number and compare to the
#probability of p, if random number<p, this node will be infected and return the value of 1

IC<-function(node_seed,network,Pprob, immuned_nodes){

  #prepare input for the 'calculate_value' function#
  adj_matrix <- igraph::as_adjacency_matrix(network, type = 'both')
  each_neighbors <- which(adj_matrix > 0, arr.ind = TRUE)
  each_neighbors <- split(each_neighbors[, 2], each_neighbors[, 1]) #get the neigbhour list of each node

  nNode<-vcount(network)
  node_status <- rep.int(0, nNode) #start from a healthy population
  day_infected<-vector()#Total number of infected population
  new_infected <- list()  # Record the ID of person getting infected at each time step
  immuned_nodes <- as.numeric(immuned_nodes) # convert immuned_nodes to numeric

  # Nodes that are immune
  node_status[immuned_nodes] <- 2

  day<-1
  node_status[as.numeric(node_seed)] <- 1 # infected(value=1) health(value=0)
  day_infected[day] <- sum(node_status)
  new_infected[[day]]<-node_seed #The ID of the person infected in Day 1 (Patient Zero)


  #simulate the spread of virus within 4 weeks##
  for (day in c(2:28)){
    ContagiousID<-which(node_status == 1)
    #print(ContagiousID) #инфцированные ноды
    infectedID<-unlist(lapply(ContagiousID,calculate_value,each_neighbors,Pprob))
    #print('кого заразили')
    #print(infectedID) #кого заразили
    newinfectedID<- setdiff(infectedID, which(node_status == 1))
    #print('новенькие')
    #print(newinfectedID)
    #print(newinfectedID) #вывести новых зараженных

    #Update the node status and other variables
    node_status[newinfectedID] <- 1
    day_infected[day] <- length(newinfectedID)
    #print(day_infected[day])

    new_infected[[day]]<-newinfectedID

    # Nodes that are immune
    node_status[immuned_nodes] <- 2

    day=day+1
  }
  return(day_infected)  #return the number of newly infected people by day
  #return(list(day_infected,new_infected)) #if you want to see the ID of infected ppl in each day, use this command instead
}
```
```{r}
immuned_nodes_degree <- c(54,20,110)
```
```{r}

sum(IC(107, Highschool, 0.15, immuned_nodes_degree))
```
```{r}
immuned_nodes_betweenness <- c(4,37,96)
```
```{r}
sum(IC(107, Highschool, 0.15, immuned_nodes_betweenness))

```
```{r}
plot(IC(107, Highschool, 0.15,immuned_nodes_betweenness), type = "l", col = "red", ylim = c(0, 20), xlab = "Day", ylab = "Average number of infected people")
lines(IC(107, Highschool, 0.15, immuned_nodes_degree), type = "l", col = "blue")
legend("topright", c("Highschool_betweenness", "Highschool_degree"), col = c("red", "blue"), lty = 1)

```
```{r}
IC_average_d <- function(node_seed,network,Pprob, immuned_nodes){
  n <- 100
  result <- matrix(0, nrow = 28, ncol = n)
  for (i in 1:n){
    result[, i] <- IC(node_seed,network,Pprob,immuned_nodes)
  }
  return(apply(result, 1, mean))
}
```
```{r}
sum(IC_average_d(107, Highschool, 0.15, immuned_nodes_degree))
```
```{r}
sum(IC_average_d(107, Highschool, 0.15, immuned_nodes_betweenness))
```
```{r}
plot(IC_average_d(107, Highschool, 0.15,immuned_nodes_betweenness), type = "l", col = "red", ylim = c(0, 20), xlab = "Day", ylab = "Average number of infected people")
lines(IC_average_d(107, Highschool, 0.15, immuned_nodes_degree), type = "l", col = "blue")
legend("topright", c("Highschool_betweenness", "Highschool_degree"), col = c("red", "blue"), lty = 1)
```

```{r}
sum(IC_average(19, Highschool, 0.15))
```
```{r}
IC_greedy <- function(network, Pprob, seed_node) {
  # prepare input for the 'calculate_value' function
  adj_matrix <- igraph::as_adjacency_matrix(network, type = 'both')
  each_neighbors <- which(adj_matrix > 0, arr.ind = TRUE)
  each_neighbors <- split(each_neighbors[, 2], each_neighbors[, 1]) # get the neigbhour list of each node

  # initialize variables
  n_nodes <- vcount(network)
  node_status <- rep.int(0, n_nodes) # start from a healthy population
  node_status[seed_node] <- 1 # set initial infected node
  max_infected <- 0 # initialize maximum number of infected nodes
  immune_nodes <- c() # initialize list of immune nodes

  # perform greedy search for 3 immune nodes
  for (i in c(1:122)){
    if (i == seed_node) next # skip the initial infected node
    # if (i %in% immune_nodes) next # skip nodes already identified as immune
    # node_status_copy <- node_status # make a copy of the node status vector to simulate infection
    # node_status_copy[i] <- 1 # make the current node immune
    infected_count <- sum(IC_average(i, network, Pprob)) # simulate infection and count number of infected nodes
    if (infected_count > max_infected) {
      max_infected <- infected_count # update maximum number of infected nodes
      immune_nodes <- c(i, immune_nodes) # add the current node to the list of immune nodes
      #if immune nodes>3, keep only top 3 immune nodes
      if (length(immune_nodes) > 3) immune_nodes <- immune_nodes[1:3]

      }
         #if (length(immune_nodes) > 5) immune_nodes <- immune_nodes[1:3] # keep only top 3 immune nodes
    }

  return(immune_nodes)
}

```
```{r}
greedy_nodes <- c(70, 48, 28)
sum(IC_average_d(107, Highschool, 0.15, greedy_nodes))
```
```{r}
IC_average_d(107, Highschool, 0.15, immuned_nodes_betweenness)
```
```{r}
IC_greedy(Highschool, 0.1, 107)
```
```{r}
greedy_nodes <- c(70, 48, 28)
```
```{r}
plot(IC_average_d(107, Highschool, 0.15,immuned_nodes_betweenness), type = "l", col = "red", ylim = c(0, 20), xlab = "Day", ylab = "Average number of infected people")
lines(IC_average_d(107, Highschool, 0.15, immuned_nodes_degree), type = "l", col = "blue")
lines(IC_average_d(107, Highschool, 0.15, greedy_nodes), type = "l", col = "green")
legend("topright", c("Highschool_betweenness", "Highschool_degree", "Highschool_greedy"), col = c("red", "blue", "green"), lty = 1)
```
```{r}
IC_average <- function(node_seed,network,Pprob){
  n <- 100
  result <- matrix(0, nrow = 28, ncol = n)
  for (i in 1:n){
    result[, i] <- IC(node_seed,network,Pprob)
  }
  return(apply(result, 1, mean))
}
```
```{r}
dist <- read.csv("/Users/ekaterinamazur/PycharmProjects/HN/Human_Networks/Assignment_2_kate/data/distribution.csv")

```
```{r}
IC_greedy_beef <- function(network, Pprob) {
  # prepare input for the 'calculate_value' function
  adj_matrix <- igraph::as_adjacency_matrix(network, type = 'both')
  each_neighbors <- which(adj_matrix > 0, arr.ind = TRUE)
  each_neighbors <- split(each_neighbors[, 2], each_neighbors[, 1]) # get the neigbhour list of each node

  # initialize variables
  n_nodes <- vcount(network)
  node_status <- rep.int(0, n_nodes) # start from a healthy population
  # node_status[seed_node] <- 1 # set initial infected node
  max_infected <- 0 # initialize maximum number of infected nodes
  immune_nodes <- c() # initialize list of immune nodes

  # perform greedy search for 3 immune nodes
  for (i in c(1:122)){
    # if (i == seed_node) next # skip the initial infected node
    # if (i %in% immune_nodes) next # skip nodes already identified as immune
    # node_status_copy <- node_status # make a copy of the node status vector to simulate infection
    # node_status_copy[i] <- 1 # make the current node immune
    infected_count <- sum(IC_average(i, network, Pprob)) # simulate infection and count number of infected nodes
    if (infected_count > max_infected) {
      max_infected <- infected_count # update maximum number of infected nodes
      immune_nodes <- c(i, immune_nodes) # add the current node to the list of immune nodes
      #if immune nodes>3, keep only top 3 immune nodes
      if (length(immune_nodes) > 7) immune_nodes <- immune_nodes[1:7]

      }
         #if (length(immune_nodes) > 5) immune_nodes <- immune_nodes[1:3] # keep only top 3 immune nodes
    }

  return(immune_nodes)
}
```
```{r}
highest_gred <- IC_greedy_beef(Highschool_beef, 0.15)
```
```{r}
highest_gred
```
```{r}
highest_degree <- order(degree(Highschool), decreasing = TRUE)[1:7]
highest_betweenness <- order(betweenness(Highschool), decreasing = TRUE)[1:7]

```
```{r}
ThModel()
```

```{r}
ThModel(highest_gred, Highschool_beef, 0.15)
```
```{r}
ThModel(highest_degree, Highschool_beef, 0.15)
```
```{r}
ThModel(highest_betweenness, Highschool_beef, 0.15)

```
```{r}
#plot TH model for the highest degree nodes, highest betweenness nodes, and highest greedy nodes
plot(ThModel(highest_degree, Highschool_beef, 0.15), type = "l", col = "red", ylim = c(0, 20), xlab = "Day", ylab = "Average number of infected people")
lines(ThModel(highest_betweenness, Highschool_beef, 0.15), type = "l", col = "blue")
lines(ThModel(highest_gred, Highschool_beef, 0.15), type = "l", col = "green")
```


