## Lab assignment 2: Social network analysis and modeling

```{r}
library('igraph')
library('network')
library('intergraph')
#comments
```

Type any R code in the chunk, for example:
```{r}
#read data from the folder data
highschool_edge<-read.csv("Assignment_2/data/Highschool_network_edge.csv")
highschool_att <- read.csv("Assignment_2/data/Highschool_network_att.csv")
facebook_att <- read.csv("Assignment_2/data/Facebook_network_att.csv")
facebook_edge <- read.csv("Assignment_2/data/Facebook_network_edge.csv")
```

```{r}
#build high school network
highschool_nodes<-data.frame(name=as.character(highschool_att$NodeID),
                  gender=as.character(highschool_att$Gender),
                  hall=as.character(highschool_att$Hall))
highschool_edges<-data.frame(from=c(as.character(highschool_edge[,1])),
                  to=c(as.character(highschool_edge[,2])))
Highschool<-graph_from_data_frame(highschool_edges,directed = FALSE,vertices = highschool_nodes)
co <- components(Highschool)
Highschool <- induced.subgraph(Highschool, which(co$membership == which.max(co$csize))) #use only the largest component for analysis
summary(Highschool)

#build facebook network
facebook_nodes<-data.frame(name=as.character(facebook_att$NodeID))
facebook_edges<-data.frame(from=c(as.character(facebook_edge[,1])),
                           to=c(as.character(facebook_edge[,2])))
Facebook<-graph_from_data_frame(facebook_edges,directed = FALSE,vertices = facebook_nodes)
summary(Facebook)
```


```{r}

#function to visualize the network (with interaction)
library(visNetwork)
set.seed(100)
Highschool_interactive_layout<-visNetwork(data.frame(id=V(Highschool)$name), highschool_edges, main = "Highschool",submain="Can zoom in/out to check the IDs and ties") %>%
  visIgraphLayout(layout = "layout_nicely",smooth =  FALSE) %>%
  visNodes(shape="circle",label = TRUE) %>%
  visOptions(highlightNearest = list(enabled = T, hover = T), nodesIdSelection = T)

Highschool_interactive_layout

```
```{r}

# find the node of he hisghest degree
#degree(Highschool)
which.max(degree(Highschool))
V(Highschool)[which.max(degree(Highschool))]

```
```{r}
#find the node of the highest betweenness centrality
#
which.max(betweenness(Highschool))
V(Highschool)[which.max(betweenness(Highschool))]

```
```{r}
#find the node of the highest closeness centrality
#closeness(Highschool)
which.max(closeness(Highschool))
V(Highschool)[which.max(closeness(Highschool))]

```
```{r}
#find the node with the highest eigen
which.max(as.numeric(unlist(eigen_centrality(Highschool))))


```
Question 2 (5 points):
•	Study the correlations between a) degree and betweenness, b) degree and closeness, c) degree and eigenvector for all the nodes in the Highschool network;
•	Study the correlations between a) degree and betweenness, b) degree and closeness, c) degree and eigenvector for all the nodes in the Facebook network;
•	From the above results, how well do different metrics correlate with each other? Which centrality metric will you use and why?
Please provide more than just a correlation coefficient to answer Question 2. You are suggested to study the correlations by developing a scatter plot as below, in which every dot represents a node in the network, with xlab as degree and ylab as closeness.
```{r}
#check the correlation between degree and betweenness
cor.test(degree(Highschool),betweenness(Highschool))
```
```{r}
#check the correlation between degree and closeness
cor.test(degree(Highschool),closeness(Highschool))
```
```{r}
#check the correlation between degree and eigenvector
cor.test(degree(Highschool),eigen_centrality(Highschool))
```
```{r}
#check the correlation between degree and betweenness
cor.test(degree(Facebook),betweenness(Facebook))
```
```{r}
#check the correlation between degree and closeness
cor.test(degree(Facebook),closeness(Facebook))
```
```{r}
#check the correlation between degree and eigenvector and add the trand line
cor.test(degree(Facebook),eigen_centrality(Facebook))
```
```{r}
# cor.test(degree(Facebook),eigen_centrality(Facebook))
#add the trand line to the plot
# abline(lm(degree(Highschool)~betweenness(Highschool)),col="red")

#make a scatter plot for degree and closeness and add the trand line to it
plot(degree(Highschool),closeness(Highschool),xlab="degree",ylab="closeness")
abline(lm(closeness(Highschool)~degree(Highschool)),col="red")
```
```{r}
#make a scatter plot for degree and closeness for Facebook
plot(degree(Facebook),closeness(Facebook),xlab="degree",ylab="closeness")
abline(lm(closeness(Facebook)~degree(Facebook)),col="red")
```
```{r}
# calculate the shortest path lengths between every pair of two nodes in Highschool network

distances(
  Highschool,
  v = V(Highschool),
  to = V(Highschool),
  mode = c("all", "out", "in"),
  weights = NULL) #Shortest path lengths between every pair of two nodes in the network

```
```{r}
#make a histogram of the shortest path lengths between every pair of two nodes in Highschool network with percentiles
hist(distances(Highschool),xlab="shortest path length",ylab="frequency",main="Histogram of the shortest path lengths between every pair of two nodes in Highschool network",breaks=100,prob=T)
```
```{r}
#make a histogram of degree distribution in Highschool network with percentiles
hist(degree(Highschool),xlab="degree",ylab="frequency",main="Histogram of degree distribution in Highschool network",breaks=100,prob=T)
```

Test the above hypothesis by the following steps (Question 4, 4 points):
```{r}
#visualize the Highschool network by gender
## visualize the network by gender###
library(RColorBrewer)
coul  <- brewer.pal(length(unique( V(Highschool)$gender)), "Set2")
my_color <- coul[as.numeric(as.factor(V(Highschool)$gender))]
set.seed(10)
plot(Highschool, vertex.color = my_color,
     vertex.size=5,
     layout=layout.fruchterman.reingold(Highschool),vertex.label=NA,
     main="Highschool network by gender")
legend("bottomleft", legend=levels(as.factor(V(Highschool)$gender)) ,col = coul , bty = "n", pch=20 , pt.cex = 1.5, cex = 1.5, horiz = FALSE, inset = c(0.1, 0.1))






```
```{r}
#introduce subgraph by gender, calculate their edge densities
group <- as.factor(unique(V(Highschool)$gender))
sapply(levels(group), function(x) {
  y <- induced_subgraph(Highschool, which(V(Highschool)$gender==x))
  paste0("Density for ", x, " friends is ", edge_density(y))
})

```
Question 5 (4 points):
1)	Calculate the modularity of the Highschool network if community is merely identified by a) gender and b) residential hall, respectively.
2)	Search the Louvain Community Detection and explain the algorithm in your own words.
3)	Use the Louvain Community Detection to identify communities in the Highschool network. Compare the modularity value produced by the Louvain algorithm to those in 1), and explain the reasons for the differences.
```{r}
### customize community by gender ###
genderCommunity<-V(Highschool)$gender
genderCommunity<-replace(genderCommunity,genderCommunity=="female",1)
genderCommunity<-replace(genderCommunity,genderCommunity=="male",2)
genderCommunity<-replace(genderCommunity,genderCommunity=="unknown",3)
genderCommunity<-as.numeric(genderCommunity)

gender.clustering <- make_clusters(Highschool, membership=genderCommunity)
modularity(gender.clustering)

### Louvain algorithm ###
Louv<-cluster_louvain(graph.object)
modularity(Louv)

```
